Paper Analysis

### 2025-01-13 Paper_WriteUp/Paper_Plots.qmd
add Sydney's code to the paper plots file

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)
library(ggdist)
library(viridis)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

```{r figure 1}

>>>>

library(tidyverse)
library(RcppRoll)
library(cmdstanr)
library(posterior)
library(bayesplot)
library(loo)
library(scales)
library(ggridges)
library(here)
library(ggdist)
library(viridis)
library(PlayerRatings)
library(ggrepel)
library(ggpubr)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

@@

```{r figure 1}
player_cohort_1 <- "sandro2502"

path_id <- 1  ## for 1700-1900 
data_path <- all_data_path[path_id]
files <- list.files(data_path)
lichess_data <- files |> 
  map_dfr(~read_player(data_path, .x))

bullet_data_fig_1 <- lichess_data |> 
  mutate(Event = tolower(Event)) |>
  filter(Variant == "Standard") |>
  filter(grepl("rated bullet game", Event))
rm(lichess_data)

p1 <- bullet_data |> 
  filter(Username == player_cohort_1)

p1$newELO <- ifelse(p1$White == paste0(player_cohort_1),
                    p1$WhiteElo, p1$BlackElo)
# p1$datetime <- as.POSIXct(paste(p1$UTCDate, p1$UTCTime),
#                           format = "%Y.%m.%d %H:%M:%S")
ltypes <- c(1, 2, 3, 1, 2, 3, 1, 2, 3, 1, 2, 3)
thetitle <- paste0("Player From 1700-1900 Cohort")
linewd <- 1
ylim1 <- 1200
ylim2 <- 3500
ndays <- 1

p1_sorted <- p1 |> arrange(UTCDate, UTCTime)
p1_sorted$event <- 1:nrow(p1_sorted)

tidy_plot1 <- ggplot(p1_sorted, aes(x = event, y = newELO)) +
  # scale_colour_manual(values = getPalette(colourCount)) +
  scale_linetype_manual(values = ltypes) +
  xlab("Games Played") +
  ylab("Lichess Rating") +
  ggtitle(thetitle) +
  ylim(ylim1, ylim2) +
  geom_line(lwd = linewd) +
  theme(
    plot.title = element_text(hjust = 0, vjust = 1, size = rel(1.7)),
    panel.background = element_blank(),
    plot.background = element_blank(),
    panel.grid.major.y = element_line(color = "gray75", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size = rel(1.1)),
    text = element_text(color = "gray20", size = 10),
    axis.text = element_text(size = rel(1.0)),
    axis.text.x = element_text(color = "gray20", size = rel(1.0)),
    axis.text.y = element_text(color = "gray20", size = rel(1.0)),
    axis.title.x = element_text(size = rel(1.0), vjust = 0),
    axis.title.y = element_text(size = rel(1.0), vjust = 1),
    axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "none"
  )

player_cohort_gm <- "alireza2003"

## load in the GM data for this
path_id <- 4  ## for GM 
data_path <- all_data_path[path_id]
files <- list.files(data_path)
lichess_data <- files |> 
  map_dfr(~read_player(data_path, .x))

bullet_data_fig_1_gm <- lichess_data |> 
  mutate(Event = tolower(Event)) |>
  filter(Variant == "Standard") |>
  filter(grepl("rated bullet game", Event))
rm(lichess_data)

p2 <- bullet_data_fig_1_gm |> 
  filter(Username == player_cohort_gm)

p2$newELO <- ifelse(p2$White == paste0(player_cohort_gm),
                    p2$WhiteElo, p2$BlackElo)
thetitle <- paste0("Player From GM Cohort")
p2_sorted <- p2 |> arrange(UTCDate, UTCTime)
p2_sorted$event <- 1:nrow(p2_sorted)

tidy_plot2 <- ggplot(p2_sorted, aes(x = event, y = newELO)) +
  # scale_colour_manual(values = getPalette(colourCount)) +
  scale_linetype_manual(values = ltypes) +
  xlab("Games Played") +
  ylab("Lichess Rating") +
  ggtitle(thetitle) +
  ylim(ylim1, ylim2) +
  geom_line(lwd = linewd) +
  theme(
    plot.title = element_text(hjust = 0, vjust = 1, size = rel(1.7)),
    panel.background = element_blank(),
    plot.background = element_blank(),
    panel.grid.major.y = element_line(color = "gray75", linetype = "dotted"),
    panel.grid.major.x = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size = rel(1.1)),
    text = element_text(color = "gray20", size = 10),
    axis.text = element_text(size = rel(1.0)),
    axis.text.x = element_text(color = "gray20", size = rel(1.0)),
    axis.text.y = element_text(color = "gray20", size = rel(1.0)),
    axis.title.x = element_text(size = rel(1.0), vjust = 0),
    axis.title.y = element_text(size = rel(1.0), vjust = 1),
    # axis.ticks.y = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "none"
  )

tdy1 <- tidy_plot1 + theme_single_y()
tdy2 <- tidy_plot2 + theme_single_y()

tidy_plot <- ggarrange(tdy1, tdy2)

ggsave(paste0(newfilename, ".png"), tidy_plot,
  dpi = 600, height = 5, width = 12
)
ggsave(plot = tidy_plot, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "elo_plot_2_players.png")), dpi = 600,
       height = 5, width = 12)
```
